APPENDIX: `{peacesciencer}`: An R Package for Quantitative Peace Science Research

### 2022-01-15 manuscript/appendix.Rmd
update, mostly Fira Code

---
title: "APPENDIX: `{peacesciencer}`: An R Package for Quantitative Peace Science Research"
# author:
# - name: Steven V. Miller
#   affiliation: Clemson University
#   email: svmille@clemson.edu
# thanks: "This is a work in progress. Feedback welcome: svmille@clemson.edu."
bibliography: "`r paste0(Sys.getenv('HOME'),'/Dropbox/master.bib')`"
biblio-style: apsr
geometry: margin=1in
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
keywords: "software, statistical analysis, peace science, reproducibility"
endnotes: FALSE
csl: inst/jpr.csl
mainfont: cochineal
sansfont: Linux Biolinum O
sansitup: FALSE
params:
  anonymous: ""
  doublespacing: ""
  removetitleabstract: ""
appendix: TRUE
appendixletter: "A"
pandocparas: TRUE
anonymous: "`r params$anonymous`"
doublespacing: "`r params$doublespacing`"
removetitleabstract: "`r params$removetitleabstract`"
linkcolor: black
nocite: |
  @cartersmith2020fml, @andersetal2020bbgb
header-includes:
  - \usepackage{longtable}
  - \usepackage{csquotes}
  - \LTcapwidth=.95\textwidth
  - \linespread{1.05}
  - \usepackage{hyperref}
  - \usepackage{setspace}
  - \renewcommand{\thepage}{A-\arabic{page}}
---

>>>>

---
title: "APPENDIX: `{peacesciencer}`: An R Package for Quantitative Peace Science Research"
author:
- name: Steven V. Miller
  affiliation: Clemson University
  email: svmille@clemson.edu
# thanks: "This is a work in progress. Feedback welcome: svmille@clemson.edu."
bibliography: "`r paste0(Sys.getenv('HOME'),'/Dropbox/master.bib')`"
biblio-style: apsr
geometry: margin=1in
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
keywords: "software, statistical analysis, peace science, reproducibility"
endnotes: FALSE
csl: inst/jpr.csl
mainfont: cochineal
sansfont: Linux Biolinum O
monofont: Fira Code
sansitup: FALSE
params:
  anonymous: ""
  doublespacing: ""
  removetitleabstract: ""
appendix: TRUE
appendixletter: "A"
pandocparas: TRUE
anonymous: "`r params$anonymous`"
doublespacing: "`r params$doublespacing`"
removetitleabstract: "`r params$removetitleabstract`"
linkcolor: black
nocite: |
  @cartersmith2020fml, @andersetal2020bbgb
header-includes:
  - \usepackage{longtable}
  - \usepackage{csquotes}
  - \LTcapwidth=.95\textwidth
  - \linespread{1.05}
  - \usepackage{hyperref}
  - \usepackage{setspace}
  - \renewcommand{\thepage}{A-\arabic{page}}
---
